---
title: "SER"
output: html_document
---

Libraries:
```{r}
source("setup.R")
```

Functions:
```{r}
#Use park code to select park of interest
get_select_parks <- function(park_code) {
  all_parks <- getParkSystem()
  all_parks %>%
    filter(UNIT_CODE == park_code)
}

#buffer park of interest 
get_aoi <- function(select_parks, buffer_dist) {
  select_parks %>%
    st_buffer(buffer_dist) %>%
    summarize()
}

#get buildings for park of interest
get_buildings <- function(parks, buffer_dist) {
  getBuildings(park_boundary = parks %>%
                 st_buffer(buffer_dist))
}

#select specific buildings by name and column name
get_select_buildings <- function(buildings, bldg_name, column_name) {
  buildings %>%
    st_transform(crs = st_crs(4326)) %>%
    filter(grepl(bldg_name, {{ column_name }}, ignore.case = TRUE)) %>%
    mutate(centroid = st_centroid(geometry)) %>%
  mutate(longitude = st_coordinates(centroid)[, 1],  
         latitude = st_coordinates(centroid)[, 2]) %>%
  select(longitude, latitude, everything())
}

#load csv data
load_csv <- function(path, x, y, crs) {
  data <- read_csv(path) %>%
    drop_na(c(x, y)) %>%
    st_as_sf(coords = c(x, y), crs = crs, remove = FALSE)
}

#transform coordinates to WGS 84
transform_wgs84 <- function(sf) {
    sf %>%
    st_transform(crs = 4326) %>%
      mutate(
        longitude_wgs84 = st_coordinates(.)[, 1],
        latitude_wgs84 = st_coordinates(.)[, 2])
}

#filter to aoi
filter_aoi <- function(data) {
  data %>%
  st_filter(aoi %>%
              st_transform(st_crs(data)))
}
```

Create objects for select park, state, aoi, and buildings:
```{r}
park <- get_select_parks("CACO")

aoi <- get_aoi(park, 1000)

buildings <- get_buildings(park, 1000)
 
select_buildings <- get_select_buildings(buildings, "g", BLDGNAME)
```

Create maps:
```{r}
a <- mapview(park,
             alpha.regions = 0.2,
             col.regions = "seagreen",
             layer.name = "Park Boundary") +
  mapview(aoi, 
          alpha.regions = 0.25,
          col.regions = "yellow",
          layer.name = "AOI") #+
  # mapview(buildings %>% st_centroid (),
  #         col.regions = "lightpink",
  #         layer.name = "Buildings") #+
  # mapview(select_buildings %>% st_centroid(),
  #         col.regions = "tomato",
  #         cex = 8,
  #         layer.name = "Select Buildings")

b <- a +
  mapview(ma_select_wells,
          col.regions = "dodgerblue",
           cex = 5,
          layer.name = 'USGWD') +
  mapview(ma_select_pws,
          col.regions = "purple",
          cex = 5,
          layer.name = "State PWS") +
  mapview(historic_building,
          col.regions = "orange",
          cex = 5,
          layer.name = "Select Buildings") #+
   # mapview(ma_select_places,
   #               col.regions = "hotpink",
   #               layer.name = "Water Sources")
  # mapview(ma_select_places,
  # col.regions = "plum",
  # cex = 5,
  # layer.name = "Buildings")

b
```

Massachusetts - read and select data:
```{r}
ma_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Massachusetts.csv", "Longitude", "Latitude", crs = 4269)
ma_wells <- transform_wgs84(ma_wells)
ma_select_wells <- filter_aoi(ma_wells)

ma_pws_path <- "data/Water_supply_Systems/data_sources/Massachusetts/MA_PWS"
ma_pws <- st_read(ma_pws_path)
ma_pws <- transform_wgs84(ma_pws)
ma_select_pws <- filter_aoi(ma_pws)

ma_historic_path <- "data/Water_Supply_Systems/data_sources/Massachusetts/ma_historic_places"
ma_historic_places <- st_read(ma_historic_path)
ma_historic_places <- transform_wgs84(ma_historic_places)
ma_select_places <- filter_aoi(ma_historic_places)

pws_point <- ma_pws %>%
  filter(grepl("height", SITE_NAME, ignore.case = TRUE))

historic_building <- ma_select_places %>%
  filter(grepl("rowell house", COMMON_NAM, ignore.case = TRUE) | grepl("rowell house", HISTORIC_N, ignore.case = TRUE))
```


Alabama - read an select data:
```{r}
al_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Alabama.csv", "Longitude", "Latitude", crs = 4269)
al_wells <- transform_wgs84(al_wells)
al_select_wells <- filter_aoi(al_wells)

al_wells_state <- load_csv("data/Water_Supply_Systems/data_sources/Alabama/Water_Wells.csv", "Longitude27", "Latitude27", crs = 4326)
```

Florida - read and select data:
```{r}
fl_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Florida.csv", "Longitude", "Latitude", crs = 4269)
fl_wells <- transform_wgs84(fl_wells)
fl_select_wells <- filter_aoi(fl_wells)

fl_wells_state <- load_csv("data/Water_Supply_Systems/data_sources/Florida/SWF_wells.csv", "XCOORD", "YCOORD", crs = 2236)
fl_wells_state <- transform_wgs84(fl_wells_state)
fl_select_wells_state <- filter_aoi(fl_wells_state)
  #dplyr::filter(grepl("name", column_name, ignore.case = TRUE)) #optional filter
  
fl_pws <- load_csv("data/Water_Supply_Systems/data_sources/Florida/PWS_non_federal.csv", "X", "Y", crs = 6439)
fl_pws <- transform_wgs84(fl_pws)
fl_select_pws <- filter_aoi(fl_pws)
  #dplyr::filter(grepl("name", column_name, ignore.case = TRUE)) #optional filter
```

Georgia
```{r}
ga_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Georgia.csv", "Longitude", "Latitude", crs = 4269)
ga_wells <- transform_wgs84(ga_wells)
ga_select_wells <- filter_aoi(ga_wells)
```

Kentucky
```{r}
ky_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Kentucky.csv", "Longitude", "Latitude", crs = 4269) 
ky_wells <- transform_wgs84(ky_wells)
ky_select_wells <- filter_aoi(ky_wells)

ky_wells_state <- read_excel("data/Water_Supply_Systems/data_sources/Kentucky/KY_WaterWellData_01.17.2023.xlsx") 
ky_wells_state <- ky_wells_state %>%
  drop_na(c(LongDecimal, LatDecimal)) %>%
  st_as_sf(coords = c("LongDecimal", "LatDecimal"), crs = 4326, remove = FALSE)
ky_wells_state <- transform_wgs84(ky_wells_state)
ky_select_wells_state <- filter_aoi(ky_wells_state)
```

Maine - read and select data:
```{r}
me_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Maine.csv", "Longitude", "Latitude", crs = 4269)
me_wells <- transform_wgs84(me_wells)
me_select_wells <- filter_aoi(me_wells)

me_wells_state <- load_csv("data/Water_Supply_Systems/data_sources/Maine/ME_Wells.csv", "Longitude", "Latitude", crs = 4326)
me_select_wells_state <- filter_aoi(me_wells_state)

#ACAD small scale GIS
acad_wqgis_path <- "data/Water_Supply_Systems/data_sources/Maine/acad_wqgis"
acad_layers <- st_layers(acad_wqgis_path)
acad_dg <- st_read(acad_wqgis_path, layer = "idg_station", crs = 26719)
acad_wq <- st_read(acad_wqgis_path, layer = "wq_station", crs = 26719)
mapview(acad_dg) + mapview(acad_wq)
```

Mississippi - read and select data:
```{r}
ms_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Mississippi.csv", "Longitude", "Latitude", crs = 4269)
ms_wells <- transform_wgs84(ms_wells)
ms_select_wells <- filter_aoi(ms_wells)

ms_wells_state <- read_sf("data/Water_Supply_Systems/data_sources/Mississippi/DEQ_Wells_24/MS_WaterWells_Nov2024.shp")
ms_wells_state <- transform_wgs84(ms_wells_state)
ms_select_wells_state <- filter_aoi(ms_wells_state) 

ms_wells_state_2 <- read_sf("data/Water_Supply_Systems/data_sources/Mississippi/DEQ_Wells_09/MS_OLWRPermittedWells_2009.shp")
ms_wells_state_2 <- transform_wgs84(ms_wells_state_2)
ms_select_wells_state_2 <- filter_aoi(ms_wells_state_2) #%>%
    #dplyr::filter(grepl("little mountain", PWS_NAME, ignore.case = TRUE)) #optional filter
```

North Carolina - read and select data:
```{r}
nc_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_North_Carolina.csv", "Longitude", "Latitude", crs = 4269)
nc_wells <- transform_wgs84(nc_wells)
nc_select_wells <- filter_aoi(nc_wells)

nc_pws <- load_csv("data/Water_Supply_Systems/data_sources/North_Carolina/Public_Water_Supply_Water_Sources.csv", "X", "Y", crs = 32119)
nc_pws <- transform_wgs84(nc_pws)
nc_select_pws <- filter_aoi(nc_pws)
  #dplyr::filter(grepl("name", column_name, ignore.case = TRUE)) #optional filter
```

South Carolina - read and select data:
```{r}
sc_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_South_Carolina.csv", "Longitude", "Latitude", crs = 4269)
sc_wells <- transform_wgs84(sc_wells)
sc_select_wells <- filter_aoi(sc_wells)
  
sc_pws <- load_csv("data/Water_Supply_Systems/data_sources/South_Carolina/SC_PWS.csv", "x", "y", crs = 26917)
sc_pws <- transform_wgs84(sc_pws)
sc_select_pws <- filter_aoi(sc_pws)
  #dplyr::filter(grepl("name", column_name, ignore.case = TRUE)) #optional filter
```

Tennessee - read and select data:
```{r}
tn_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Tennessee.csv", "Longitude", "Latitude", crs = 4269)
tn_wells <- tranform_wgs(tn_wells)
tn_select_wells <- filter_aoi(tn_wells)

tn_wells_state <- load_csv("data/Water_Supply_Systems/data_sources/Tennessee/Water_Wells.csv", "X", "Y", crs = 4326)
tn_select_wells_state <- filter_aoi(tn_wells_state)
  #dplyr::filter(grepl("name", column_name, ignore.case = TRUE)) #optional filter
```

Virginia - read and select data:
```{r}
va_wells <- load_csv("data/all/Water_Supply/USGWD-Tabular/USGWD_Virginia.csv", "Longitude", "Latitude", crs = 4269)
va_wells <- transform_wgs84(va_wells)
va_select_wells <- filter_aoi(va_wells)
```

Import Water Supply Database
```{r}
table_path <- "data/Water_Supply_Systems/NPS_Water_Systems_Database_Joined.xlsx" 

source_table <- read_excel(table_path, sheet = 1, na = "NA", skip = 1) 

source_table <- source_table %>%
  mutate(
    source_longitude = as.numeric(trimws(as.character(source_longitude))),
    source_latitude = as.numeric(trimws(as.character(source_latitude)))
  ) %>%
  filter(!is.na(source_longitude) & !is.na(source_latitude))

source_table_locs <- st_as_sf(
  source_table,
  coords = c("source_longitude", "source_latitude"),
  crs = 4326,
  remove = FALSE
) 


select_source_region <- source_table_locs %>%
  dplyr::filter(region == "Northeast Region")

select_source_state <- source_table_locs %>%
  dplyr::filter(state == "MA") 

c <-mapview(select_source_region,
                 col.regions = "hotpink",
                 layer.name = "Water Sources")

d <- mapview(select_source_state,
                 col.regions = "hotpink",
                 layer.name = "Water Sources")

parks_state <- getParkSystem() %>%
  filter(STATE == "MA")

e <- d + mapview(parks_state) 

# e <- mapview(tn_select_wells) + mapview(tn_select_wells_state) + mapview(select_source_region,
#                  col.regions = "hotpink",
#                  layer.name = "Water Sources")

e
```

View and Tidy
```{r}
# look at what is in the columns
## glimpse()
select_source_region %>%
  glimpse()
## slice()
select_source_region %>%
  slice()
## head()
select_source_region %>%
  head()

# remove sources that are not in use
active_SER <- select_source_region %>%
  filter(in_use == "Yes")

# map by system_type
mapview(
  select_source_region,
  zcol = "system_type",
  label = paste("System Type:", active_SER$system_type, "<br>",
                "Source Type:", active_SER$source_type))

# map by source_state
mapview(
  select_source_region,
  zcol = "source_state")

# map by source_type
mapview(
  select_source_region,
  zcol = "source_type")

# map by source_location_refs
mapview(
  select_source_region,
  zcol = "source_location_refs")

select_source_region$source_location_refs <- sub(",.*", "", select_source_region$source_location_refs)

mapview(
  select_source_region,
  zcol = "source_location_refs")

# map by use_category
mapview(
  select_source_region,
  zcol = "use_category")
```

